\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-16 bare_conf.tex
Update bare_conf.tex
the affiliation part was changed (the two working places are not changed)
Please, provide an example of this issue

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{\IEEEauthorblockN{Povilas Daniu\v{s}is\IEEEauthorrefmark{1},
Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3} and 
Darius Plikynas\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Vilnius Gediminas Technical University,\\
Vilnius, Lithuania.
}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Norwegian Centre for E-health Research, University Hospital of North Norway,\\
Troms\o, Norway.}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Nature Research Center,\\ 
Vilnius, Lithuania.
}}

>>>>

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Povilas Daniu\v{s}is\IEEEauthorrefmark{1},
%Andrius Budrionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
%Audrius Indriulionis\IEEEauthorrefmark{1}\IEEEauthorrefmark{3} and 
%Darius Plikynas\IEEEauthorrefmark{1}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}Vilnius Gediminas Technical University,\\
%Vilnius, Lithuania.
%}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Norwegian Centre for E-health Research, University Hospital of North Norway,\\
%Troms\o, Norway.}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Nature Research Center,\\ 
%Vilnius, Lithuania.
%}}

\author{
\begin{tabular}[t]{c@{\extracolsep{2em}}c} 
Povilas Daniu\v{s}is & Audrius Indriulionis \\
{\scriptsize Department of Business Technologies  and Entrepreneurship }& {\scriptsize Department of  of Business Technologies and Entrepreneurship}\\ 
{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize Vilnius Gediminas Technical University}\\
{\scriptsize Vilnius, Lithuania} & {\scriptsize Vilnius, Lithuania}\\
{\scriptsize email: povilas.daniusis@vgtu.lt} & {\scriptsize email: audrius.indriulionis@vgtu.lt} \\
& \\
Andrius Budrionis & Darius Plikynas \\
{\scriptsize Norwegian Centre for E-health Research} & {\scriptsize Department of Business Technologies and Entrepreneurship}\\ 
{\scriptsize University Hospital of North Norway} & {\scriptsize Vilnius Gediminas Technical University}\\
{\scriptsize Troms\o, Norway} & {\scriptsize Vilnius, Lithuania}\\
{\scriptsize email: andrius.budrionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\
\end{tabular}
}
